### 2020-12-04 booklet-tex/introduction.tex
Make room for a new booklet

Starting small, the next example shows three different
approaches to define the addition of three \verb|SmallInteger| objects toward 
the introduction of the relational paradigm.
\begin{example}
In math a relation $P$ is usually characterized by a statement such as
\begin{displaymath}
\forall a,b,c.\,P(a,b,c) \leftrightarrow a + b = c \quad\text{from which}\quad
P(1,2,3) \quad\text{can be proved.}
\end{displaymath}
The same check can be expressed in Smalltalk using either the
\textit{imperative style}
\begin{minted}[fontsize=\footnotesize]{smalltalk}
a := 1.  b := 2.  c := a + b.  Object assert: [ c = 3 ]
\end{minted}
or the \textit{functional style}
\begin{minted}[fontsize=\footnotesize]{smalltalk}
Object assert: [ ([ :a :b | a + b ] value: 1 value: 2) = 3 ]
\end{minted}
or, finally, the \textit{declarative style}
\begin{minted}[fontsize=\footnotesize]{smalltalk}
Object assert: [ [ :a :b :c | a + b = c ] value: 1 value: 2 value: 3 ]
\end{minted}
which closely resembles the mathematical statement.
\end{example}

>>>>

Starting small, the next example shows three different
approaches to define the addition of three \ct{SmallInteger} objects toward 
the introduction of the relational paradigm.
\begin{example}
In math a relation $P$ is usually characterized by a statement such as
\begin{displaymath}
\forall a,b,c.\,P(a,b,c) \leftrightarrow a + b = c \quad\text{from which}\quad
P(1,2,3) \quad\text{can be proved.}
\end{displaymath}
The same check can be expressed in Smalltalk using either the
\textit{imperative style}
\begin{minted}[fontsize=\footnotesize]{smalltalk}
a := 1.  b := 2.  c := a + b.  Object assert: [ c = 3 ]
\end{minted}
or the \textit{functional style}
\begin{minted}[fontsize=\footnotesize]{smalltalk}
Object assert: [ ([ :a :b | a + b ] value: 1 value: 2) = 3 ]
\end{minted}
or, finally, the \textit{declarative style}
\begin{minted}[fontsize=\footnotesize]{smalltalk}
Object assert: [ [ :a :b :c | a + b = c ] value: 1 value: 2 value: 3 ]
\end{minted}
which closely resembles the mathematical statement.
\end{example}
